A Detailed Analysis of Performance Bottlenecks in MRI Pre-Processing

### 2023-08-11 paper/paper.tex
latest change to paper and experiments.

\usepackage{cite}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=blue,filecolor=black,urlcolor=blue}
\usepackage{graphicx}
\graphicspath{{figures}}
\usepackage{listings}
\renewcommand{\lstlistingname}{Algorithm}
\usepackage[binary-units=true]{siunitx}

@@

\section{Introduction}
Magnetic Resonance Imaging (MRI) is a standard tool used by neuroscientists to perform clinical diagnosis and for researchers to develop a better understanding of the brain. Three main MRI techniques exist: structural MRI (sMRI), functional MRI (fMRI), and diffusion MRI (dMRI). While other modalities such as EEG, CT, and PET exist, we focus on MRIs for their broad adoption and non-invasive property. However, MRI data analysis is challenging due to computationally expensive pre-processing and large output and intermediate data size.

Neuroscientists developed various toolboxes to tackle the challenging task of pre-processing MRI data. Among those, some openly available and commonly accepted emerged: AFNI~\cite{Cox1996-sl}, ANTs~\cite{Avants_undated-fu}, FreeSurfer~\cite{Fischl2012-bp}, FSL~\cite{Jenkinson2012-cq}, and SPM~\cite{Friston2007-ag}. While the previous pipelines focus on specific steps of MRI pre-processing, tools like fMRIPrep~\cite{Esteban2019-og} and DIPY~\cite{Garyfallidis2014-ve} combine various pipelines to produce a complete pre-processing workflow.

The MRI pre-processing of a subject can take several hours, preventing the clinical use where data analysis might be required in timely manner. The lengthy pre-processing hinders researchers with limited computational resources to perform research on large cohorts.

@@

To the best of our knowledge, there is no comprehensive study of the bottlenecks in MRI pre-processing. In this paper, we characterize computational and I/O cost of several commonly adopted MRI pre-processing pipelines. The results of our analysis serve as a reference for future efforts to optimize the MRI pre-processing workflow.

\section{Background}

\subsection{MRI Pre-Processing}
% Look at the benchamrked tool and the information needed to abstract those tools.
% Discussion of the pre-processing steps.
% Explain their computation and I/O requirements.

% sMRI

% fMRI

% dMRI

\subsection{Intel VTune profiler}
% Requirements for profiling the Neuroimaging field.
% Multi-language support
% Lightweight
% Info on function and module runtime

% VTune

% Challenges remaining
% Debug information when compiling, for valuable information
% Combining the results from multiple analysis. Different input data can 
% vary the analysis significantly. (due to application branching and convergence)

\section{Methods}
In this section, we explain our choice of pipelines and dataset. We describe the methods used for profiling the dataset with the different applications.

For a detailed view of our methods, we redirect the reader to our GitHub repository (see Section~\ref{data-availability}), which contains the code for:

\begin{itemize}
	\item Acquiring the datasets.
	\item Building the containerized image for the pipelines.
	\item Executing the pipeline locally or on a SLURM cluster.
	\item Visualizing the profiling data.
\end{itemize}

\subsection{Pipelines}
In this analysis, we aim to cover the pre-processing performance for different MRI modalities. We study the performance bottleneck of large toolboxes and individual pipelines. We use the pipelines from the LivingPark project as a real use case of MRI pre-processing.
% TODO citation for LivingPark project. 
% Q: Ask Tristan about it.
% A: GitHub page for now
% -> Added to paperpile

First, we choose these commonly accepted workflows: fMRIPrep anatomical only without and without FreeSurfer, fMRIPrep complete workflow, and DIPY. This let us study the coarse grain performance of workflows for anatomical, functional, and diffusion MRI pre-processing.

Second, we perform a finer grain analysis of the aforementioned workflows' sub-components. The fMRIPrep anatomical workflow uses these pipelines: ANTS Brain Extraction, FSL FAST, and FreeSurfer recon-all. The fMRIPrep Bold workflow use those: AFNI 3dTShift, FSL MELODIC, FSL MCFLIRT, and FSL FLIRT. DIPY uses the following pipelines: \dots
% TODO Decide on workflow sub-components.

Last, the LivingPark project replicates several papers on Parkinson's Disease with a broad range of analysis. The study uses the following pipelines: FSL SIENA, SPM DARTEL, and SPM pairwise registration.
% TODO Validate which pipelines are used in the project.
% Ideally use all the LivingPark pipelines. If some cannot be used, explain why.

\subsection{Dataset}
To ensure the performance profile of the application derived from our work is inclusive of different population, we use dataset with a wide range of age and equal distribution of sex (biological). Using a diverse dataset should help to prevent findings of potential performance bottleneck associated to a specific population.

For the sMRI and fMRI pipelines, we use the Consortium for Reliability and Reproducibility (CoRR) dataset~\cite{Zuo2014-xa} publicly available on Datalad\footnote{\href{https://datasets.datalad.org/?dir=/corr/RawDataBIDS}{https://datasets.datalad.org/?dir=/corr/RawDataBIDS}}. The CoRR dataset contains 1629 subjects resting state fMRI (rfMRI) data (5093 rfMRI scans) collected across 18 international sites. For computational feasibility, we limit ourselves to the LMU 2 site. We chose the LMU 2 site for its diversity, with 40 subjects of age 20-79 (mean 50.8) and a female-to-male ratio of 45\%.
% Q: Might want to discuss the data size and type (anat, func, dwi).

% TODO Choose dataset for dMRI pipelines.
% CoRR has some sites with dwi data. Could use subjects from those sites.

% TODO Discuss the PPMI dataset.

\subsection{Profiling}
We use the Intel VTune profile for our analysis. On the one hand, it has a low performance overhead and offers reporting profiling data at various granularity. On the hand, it requires the debug information of an application to make sense of its profiling data. Otherwise, function names are not available. Therefore, as a first step, we re-compiled each pipeline with debug information in a Docker image. For use on HPC systems, we created Singularity images using Docker2Singularity.

\lstlistingname~\ref{vtune_example} illustrate the profiling of a pipeline by mounting the VTune binary to the Singularity image at execution. We store the profiling result for each (pipeline, subject) pair. Combining the Pareto's law and VTune bottom-up report, we identify the top 20\% of function calls that approximately account for 80\% of the pipeline execution time. This heuristic allows us to focus our efforts on the performance critical sections of a pipeline.

\lstinputlisting[
	language={bash},
	caption={Profiling an application within a Singularity container, using VTune profiler.},
	captionpos=b,
	label=vtune_example,
	numbers=left,
	frame=single,
	basicstyle=\footnotesize,
	numbersep=5pt,
	numberstyle=\tiny\color{gray},
	rulecolor=\color{black},
	tabsize=2,
]{vtune-example.sh}

Finally, the execution branching of pipeline can vary based on the input data. Therefore, we aggregate the profiling results of each pipeline across all subjects. We calculate the mean and standard deviation of total execution time of all top 20\% functions and modules of the pipeline.
% TODO Decide how the mean is calculated.
% Either total number of subjects or only with function.

% TODO explain profiling with single-thread vs. multi-thread.
We set all applications to use a single thread, while profiling. This let

\subsection{Infrastructure}
% TODO
% slashbin description
For our experiments, we used the \textit{Slashbin cluster} at Concordia University. The cluster has eight compute nodes, each configured with two 16-core Intel(R) Xeon(R) Gold 6130 CPU @ \SI{2.10}{\giga\hertz}, \SI{250}{\gibi\byte} of RAM, \SI{126}{\gibi\byte} of tmpfs, six \SI{447}{\gibi\byte} SSDs with the XFS file system (no RAID enabled), CentOS~8.1 and Linux kernel \textit{4.18.0-240.1.1.el8\_lustre.x86\_64}.

@@

The data generated by the VTune profiler is written to a shared file system, for administrative reasons. Theoretically, this increase the profiling overhead. However, in practice there is no impact since the data generated by the VTune profiler is very small.

\section{Results}
% TODO
% 2-step approach:
% 1. Which pipeline constitute the long execution time in preprocessing?
% 2. For those, which functions take the most time to execute? (hotspot)

\subsection{Makespan}
% Identify which tools take the longest to execute.

% ###    FIGURE    ###
%  Bar chart with the total makespan of the pipeline execution (mean + std)
% ### END FIGURE ####
% This will let us decided which pipeline to investigate more.

\subsection{Hotspot}
% (1-2 pages)
% TopK (approx. 10) longest makepsan application. The rest can go in supplemental.
% ###    FIGURE    ###
% (Large pipeline)
% fMRIPrep
% sMRIPrep
% DIPY
% 
% (Pipeline components)
% SPM DARTEL
% SPM pairwise registration
% ### END FIGURE ####

% Supplementary figure for the sub-components of large pipelines.
% Or include them in #(Pipeline components), if space allows.

\section{Discussion}
% TODO
% Principal Bottlenecks

% Limitation
% Can only perform profiling of open-source pipelines
% Or pipelines with debug-info.

% Opportunity for optimisation (future work)
% Reduced precision for: Compute or Compression

@@

\section{Data Availability}
\label{data-availability}
The code to compile, profile, and execute the pipelines is publicly available at:

\href{https://github.com/mathdugre/mri-bottleneck}{https://github.com/mathdugre/mri-bottleneck}
% TODO Update URL to slashbin org, when created.

@@

>>>>

\usepackage{cite}
\usepackage{xcolor}
\usepackage{hyperref}
\hypersetup{colorlinks=true,linkcolor=black,citecolor=blue,filecolor=black,urlcolor=blue}
\usepackage{graphicx}
\graphicspath{{figures}}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup[subfigure]{singlelinecheck=false, skip=0pt}
\usepackage{listings}
\renewcommand{\lstlistingname}{Algorithm}
\usepackage[binary-units=true]{siunitx}
\usepackage{csvsimple}

@@

\section{Introduction}
% Intro: Large dataset, long processing time, I/O intensive (derivatives), focus on MRI, no current study, pipelines?
% **Main question:** What are the main bottleneck in MRI pre-processing?
% **Why:** Performance of neuroimaging pipeline is critical (larger study, clinical use). However, limited study on performance profile.
Magnetic Resonance Imaging (MRI) is a standard tool used by neuroscientists to perform clinical diagnosis and for researchers to develop a better understanding of the brain. Three main MRI techniques exist: structural MRI (sMRI), functional MRI (fMRI), and diffusion MRI (dMRI). While other modalities such as EEG, CT, and PET exist, we focus on MRIs for their broad adoption and non-invasive property. However, MRI data analysis is challenging due to computationally expensive pre-processing and large output and intermediate data size.

Neuroscientists developed various toolboxes to tackle the challenging task of pre-processing MRI data. Among those, some openly available and commonly accepted emerged: AFNI~\cite{Cox1996-sl}, ANTs~\cite{Avants_undated-fu}, FreeSurfer~\cite{Fischl2012-bp}, FSL~\cite{Jenkinson2012-cq}, and SPM~\cite{Friston2007-ag}. While the previous pipelines focus on specific steps of MRI pre-processing, tools like fMRIPrep~\cite{Esteban2019-og} and dMRIPrep~\cite{Michael2021-4515513} combine various pipelines to produce a complete pre-processing workflow.

The MRI pre-processing of a subject can take several hours, preventing the clinical use where data analysis might be required in timely manner. Moreover, the lengthy pre-processing hinders researchers with limited computational resources to perform research on large cohorts.

@@

The neuroimaging community is well aware that MRI pre-precessing pipelines require long computation time. However, to the best of our knowledge, there is no comprehensive study of the performance bottlenecks in MRI pre-processing. In this paper, we characterize computational cost of several commonly adopted MRI pre-processing pipelines. The results of our analysis serve as a reference for future efforts to optimize MRI pre-processing workflows.

\section{Methods}
\subsection{Infrastructure}
For our experiments, we used the \textit{Slashbin cluster} at Concordia University. The cluster has eight compute nodes, each configured with two 16-core Intel(R) Xeon(R) Gold 6130 CPU @ \SI{2.10}{\giga\hertz}, \SI{250}{\gibi\byte} of RAM, \SI{126}{\gibi\byte} of tmpfs, six \SI{447}{\gibi\byte} SSDs with the XFS file system (no RAID enabled), CentOS~8.1 and Linux kernel \textit{4.18.0-240.1.1.el8\_lustre.x86\_64}.

\subsection{Data}
To ensure the performance profiles of the applications derived from our work are inclusive of different population, we used data with a wide range of age and equal distribution of sex (biological). Using a diverse dataset should help to prevent findings of potential performance bottleneck associated to a specific population.

We used the the OpenNeuro ds004513 v.1.0.2 dataset~\cite{ds004513:1.0.2}. The anatomical, functional, and diffusion data from 20 health individuals was acquired from two different cohorts. The within-subject cohort has nine participants (mean age=43, std=7; 4 females) with two session: eyes open and eyes closed. The replication cohort has eleven participants (mean age=27, std=5; 6 females) with only the eyes open session. We profiled the application using both cohort on the eyes open session, unless explicitly specified.

\subsection{Pipelines}
% TODO rework
In this analysis, we aim to cover the pre-processing performance for different MRI modalities. We study the performance bottleneck of large toolboxes and individual pipelines. Moreover, we use several pipelines from the LivingPark project~\cite{livingpark} as a real use case of MRI pre-processing.

First, we profile these commonly accepted workflows: fMRIPrep anatomical only without and without FreeSurfer, fMRIPrep complete workflow, and dMRIPrep. This let us study the coarse grain performance of workflows for anatomical, functional, and diffusion MRI pre-processing.

Second, we perform a finer grain analysis of the aforementioned workflows' sub-components. We list the different sub-workflow and describe the key steps for each modality in the section below.

Last, the LivingPark project replicates several papers on Parkinson's Disease with a broad range of analysis. The study uses the following pipelines: FSL SIENA/VIENA, SPM VBM, SPM DARTEL, and SPM pairwise registration.
% TODO Decide which pipelines to use from the project.

% ############################################################
% Pre-Processing
% ############################################################
% Look at the benchmarked tool and the information needed to abstract those tools.
% Discussion of the pre-processing steps.
% Explain their computation and I/O requirements.
\subsection{sMRI Pre-Processing}
\subsubsection{Intensity correction}
% NU4 bias correction (Check ANTS brainExtraction)

\subsubsection{Reference Image}
% Longitudinal study
% FreeSurfer mri_robust_template

\subsubsection{Skull-Stripping}
% ANTS brainExtraction

\subsubsection{Spatial Normalization}
% ANTS registrationSyN

\subsubsection{Segmentation}
% FSL FAST

\subsubsection{Surface Reconstruction}
% FreeSurfer recon-all

\subsection{fMRI Pre-Processing}
\subsubsection{Slice-Timing Correction}
% AFNI 3dTShift

\subsubsection{Head-Motion Correction}
% FSL MCFLIRT

\subsubsection{Susceptibility Distortion Correction}
% SDC workflow

\subsubsection{Registration}
% FSL FLIRT

\subsection{dMRI Pre-Processing}
\subsubsection{Eddy Currents Distortion Estimation}
% FSL eddy

\subsection{Profiling}
Profiling MRI pre-processing pipelines present a set of challenges. The neuroimaging community develops pipelines using several programming languages including \textit{C}, \textit{C++}, \textit{Fortran}, \textit{Python}, and \textit{Matlab}, with several pipelines utilizing a combination of multiple languages. Pipelines are generally complex and computationally expensive.

The Intel VTune profiler~\cite{vtune_profiler} satisfies these challenges by offering multi-language support, low performance overhead, and information of functions at runtime level. However, ome general profiling challenges remain. Profilers require source code to be compiled with Debug Symbols to report useful information about the different functions and modules. Moreover, different input data can substantially vary the analysis due to conditional branching in the application and convergence thresholds. We discuss our approach to these challenges in the next section.
% TODO add citation on effect of different input data on numerical stability and reduced precision.

First, to obtain human readable information on function and module names in VTune, we re-compiled each pipeline with debug information in a Docker image. For use on HPC systems, we created Singularity images using Docker2Singularity \lstlistingname~\ref{vtune_example} illustrate the profiling of a pipeline by mounting the VTune binary to the Singularity image at execution.
\lstinputlisting[
	language={sh},
	caption={Profiling an application within a Singularity container, using VTune profiler.},
	captionpos=b,
	label=vtune_example,
	numbers=left,
	frame=single,
	basicstyle=\footnotesize,
	numbersep=5pt,
	numberstyle=\tiny\color{gray},
	rulecolor=\color{black},
	tabsize=2,
]{vtune-example.sh}

Second, to estimate an average performance profile, we aggregate the profiling results of each pipeline across all subjects. Combining the Pareto's law and VTune hotspots report, we present the functions accounting for most of the CPU time up to 80\% of the total cpu time of the application. This heuristic allows us to focus our efforts on the performance critical sections of a pipeline. We report the mean and standard deviation of the execution time for those functions.

Last, we profile the application two threading configuration: single-threaded and 32 threads. On the one hand, the single-threaded approach limits the potential overhead from I/O on the profiling. On the other hand, we evaluate the multi-threading performance of the applications using maximum number of CPU core available on our system (i.e. 32).

@@

The data generated by the VTune profiler is written to a shared file system, for administrative reasons. Theoretically, this increase the profiling overhead. However, in practice there is no impact since the data generated by the VTune profiler is very small and is not written on the same file system as the data from applications.

\section{Results}
% TODO
% 2-step approach:
% 1. Which pipeline constitute the long execution time in preprocessing?
% 2. For those, which functions take the most time to execute? (hotspots)
% Any key finding: common point between functions, mem bound, fops, etc.

% In this section, analyze the aggregated profiling data obtained with VTune. First, a coarse summary of the workflows and pipelines is presented using their makespan. Second, we depict detailed analysis for the key functions contributing to the CPU time of each application (hotspots).

\subsection{Makespan}
% Identify which tools take the longest to execute.
% This will let us decided which pipeline to investigate more.
Figure~\ref{fig:makespan-1thread} shows the mean and standard deviation of the makespan, in seconds, while using 1 thread for one execution of all subjects.
Unexpectedly, we observe that both ANTS~BrainExtration and ANTS~RegistrationSyN are slower when using single precision compared to double precision.
% TODO Stat test between mean for single and double precision.
\begin{figure}[h]
	\centering
	\includegraphics[width=\linewidth]{figures/makespan-1thread.png}
	\caption{Profiling of the pipelines using 1 thread.}
	\label{fig:makespan-1thread}
\end{figure}

\subsection{Hotspots}
Figure~\ref{fig:hotspots-fmriprep-anat-subworkflow} depicts the hotspot observed from profiling the fMRIPrep anatomical sub-workflows. In each sub-figure, the x-axis shows the function ID grouped by parent module, which are ordered by CPU time of (1) the modules, then (2) the functions within a module. The function ID are found in the supplementary material Section~\ref{sec:supplementary}. The bars show the average CPU time in seconds of a function and the error bars indicate the standard deviation, with the left y-axis showing the scale. The light-green dots represent the functions cumulative percentage makespan of the application, with the right y-axis showing the scale. The color of the bar indicate the percentage of calls, for the function, that were ``stalled due to demand memory loads and stores''\footnote{\href{https://www.intel.com/content/www/us/en/docs/vtune-profiler/user-guide/2023-0/cpu-metrics-reference.html\#MEMORY-BOUND}{Vtune Memory Bound metric}}, with the left color bar showing the scale.

In figure~\ref{subfig:hotspots-ants-brainExtraction}, we observe that the function 1 and 2 account for a significant portion of the application execution time. Moreover, calls from function~1 are memory bound $51.84\pm{4.55}$ percent of the time. Table~\ref{extab:hotspots-1thread-ants-brainExtraction} shows that both functions are part of the ITK linear interpolation module.

Similarly, figure~\ref{subfig:hotspots-ants-brainExtraction-fp} shows the same two function accounting for the most time, although in flipped order. Calls from function~2 are memory bound $36.30\pm{4.98}$ percent of the time. Compared to the double precision version of ANTS brainExtraction, the third function runtime is significantly larger. It is an ITK function transforming points while calculating the displacement field of the image.

Figure~\ref{subfig:hotspots-ants-registrationSyN} and figure~\ref{subfig:hotspots-ants-registrationSyN-fp} show that the execution time for ANTS registrationSyN is dominated by a single function. In both case, the ITK function evaluating point during linear interpolation. The next two function are also shared between the application, although in flipped order. These functions show some memory bound in the range of 16--27.5. We also note the three most expensive functions are the same as in both versions of ANTS brainExtraction.

% TODO FreeSurfer 1-thread sub-figure

In figure~\ref{subfig:hotspots-32threads-freesurfer-reconall}, we observe that OMP is a major bottleneck for the application, accounting for at least 76\% of the application runtime. The only function shown from FreeSurfer recon-all is the same as the first function from figure~\ref{subfig:hotspots-1thread-freesurfer-reconall}. However, it only accounts for 2\% of the total makespan compared to 3.8\% while running sequentially.

\begin{figure*}[ht!]
	\centering
	% ANTS brainExtraction
	\begin{subfigure}[t]{0.49\textwidth}
		\caption{}
		\label{subfig:hotspots-ants-brainExtraction}
		\includegraphics[width=\textwidth]{figures/hotspots-1thread-ants-brainExtraction.png}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{0.49\textwidth}
		\caption{}
		\label{subfig:hotspots-ants-brainExtraction-fp}
		\includegraphics[width=\textwidth]{figures/hotspots-1thread-ants-brainExtraction-fp.png}
	\end{subfigure}

	% ANTS registrationSyN
	\begin{subfigure}[t]{0.49\textwidth}
		\caption{}
		\label{subfig:hotspots-ants-registrationSyN}
		\includegraphics[width=\textwidth]{figures/hotspots-1thread-ants-registrationSyN.png}
	\end{subfigure}
	\hfill
	\begin{subfigure}[t]{0.49\textwidth}
		\caption{}
		\label{subfig:hotspots-ants-registrationSyN-fp}
		\includegraphics[width=\textwidth]{figures/hotspots-1thread-ants-registrationSyN-fp.png}
	\end{subfigure}

	% FreeSurfer recon-all
	\begin{subfigure}[t]{\textwidth}
		\caption{}
		\label{subfig:hotspots-1thread-freesurfer-reconall}
		\includegraphics[width=\textwidth]{figures/hotspots-1thread-freesurfer-reconall.png}
	\end{subfigure}

	\begin{subfigure}[t]{0.49\textwidth}
		\caption{}
		\label{subfig:hotspots-32threads-freesurfer-reconall}
		\includegraphics[width=\textwidth]{figures/hotspots-32threads-freesurfer-reconall.png}
	\end{subfigure}
	\hfill
	% FSL FAST
	\begin{subfigure}[t]{0.49\textwidth}
		\caption{}
		\label{subfig:hotspots-fsl-fast}
		\includegraphics[width=\textwidth]{figures/hotspots-1thread-fsl-fast.png}
	\end{subfigure}

	\caption{Hotspots profiling of fMRIPrep's anatomical sub-workflows.}
	\label{fig:hotspots-fmriprep-anat-subworkflow}
	% TODO: Describe the plot components. Plots are quite complex so this will be necessary for proper understanding.
\end{figure*}

\begin{figure*}[ht!]
	\centering
	% FSL MCFLIRT
	\begin{subfigure}[t]{0.49\textwidth}
		\caption{}
		\label{subfig:hotspots-fsl-mcflirt}
		\includegraphics[width=\textwidth]{figures/hotspots-1thread-fsl-mcflirt.png}
	\end{subfigure}
	% FSL FLIRT
	\hfill
	\begin{subfigure}[t]{0.49\textwidth}
		\caption{}
		\label{subfig:hotspots-fsl-flirt}
		\includegraphics[width=\textwidth]{figures/hotspots-1thread-fsl-flirt.png}
	\end{subfigure}

	\caption{Hotspots profiling of fMRIPrep's functional sub-workflows.}
	\label{fig:hotspots-fmriprep-func-subworkflow}
	% TODO: Describe the plot components. Plots are quite complex so this will be necessary for proper understanding.
\end{figure*}

\section{Discussion}
% TODO

% Principal Bottlenecks
% What are common key points between the different applications?
% Possibly move this to the Results section.
% - Top 3 functions in ANTS application are the same, although in varying order.
% -

% # Limitation
% - Can only perform profiling of open-source pipelines or pipelines with debug-info.
% - No information about space or time for function call.
% - Dataset only contains healthy subjects (no pathology).
% - Dataset is from a single site. Possible bias from scanner or protocol.

% # Opportunity for optimization (future work)
% Reduced precision for: Compute or Compression. Reduce memory footprint and compute time. -> Mention the applications with high FP-ops and MEM-bound.

% # Linear Interpolation
% Theoretical improvements using reduced precision. If time permits, toy experiment with ITK single precision data type at different locations.

% # Single precision slowdown?
% Possibly due to slower convergence and less optimized code. (Quick drop-in of ITK single precision data type.)
% Need to investigate more.

% OpenOMP bottleneck (FreeSurfer with 32 threads)
% Majority of the time is spent waiting to synchronize threads.
% If times permit, changes the scheduling type and run for a subject to see if we can get performance improvements.

@@

\section{Data Availability}
\label{sec:data-availability}
The entire OpenNeuro ds004513 v1.0.2 dataset is freely available to download at:
\\\href{https://openneuro.org/datasets/ds004513/versions/1.0.2}{https://openneuro.org/datasets/ds004513/versions/1.0.2}.
% TODO add compiled containers.
% TODO add csv files from profiled runs.
% The above can be distributed on DockerHub and Zenodo respectively.

\section{Code Availability}
\label{sec:code-availability}
The code to compile, profile the pipelines, and generate figures is publicly available at:
\\\href{https://github.com/mathdugre/mri-bottleneck}{https://github.com/mathdugre/mri-bottleneck}
% TODO Update URL to slashbin org, when created.

@@

\newpage
\onecolumn
\section*{Supplementary material}
\label{sec:supplementary}

\csvnames{csvcol}{2=\module, 3=\func, 4=\mean, 5=\std}
\csvstyle{hotspot}{
	tabular = |r|l|l|c|,
	table head = \hline & Module & Function & CPU Time (mean$\pm$std)\\\hline\hline,
	late after line = \\\hline,
	respect all,
	csvcol
}
\newcommand{\csvtable}[3]{
	\begin{table}[h]
		\resizebox*{\textwidth}{!}{
			\csvreader[hotspot]{#1}{}
			% \csvreader[hotspot, filter={\value{csvrow}<60}]{#1}{}
			{\thecsvrow & \module & \func & \tablenum[round-precision=2, round-mode=places]{\mean}$\pm$\tablenum[round-precision=2, round-mode=places]{\std}}
		}
		\caption{#2}
		\label{#3}
	\end{table}
}

% CSV tables
% ANTS brainExtraction
\csvtable{tables/hotspots-1thread-ants-brainExtraction.csv}{ANTS brainExtraction (1 thread): Top functions accouting for 80\% of the application makespan.}{extab:hotspots-1thread-ants-brainExtraction}
\csvtable{tables/hotspots-1thread-ants-brainExtraction-fp.csv}{ANTS brainExtraction-fp (1 thread): Top functions accouting for 80\% of the application makespan.}{extab:hotspots-1thread-ants-brainExtraction-fp}

% ANTS registrationSyN
\csvtable{tables/hotspots-1thread-ants-registrationSyN.csv}{ANTS registrationSyN (1 thread): Top functions accouting for 80\% of the application makespan.}{extab:hotspots-1thread-ants-registrationSyN}
\csvtable{tables/hotspots-1thread-ants-registrationSyN-fp.csv}{ANTS registrationSyN-fp (1 thread): Top functions accouting for 80\% of the application makespan.}{extab:hotspots-1thread-ants-registrationSyN-fp}

% FreeSurfer recon-all
\csvtable{tables/hotspots-1thread-freesurfer-reconall.csv}{FreeSurfer recon-all (1 thread): Top functions accouting for 80\% of the application makespan.}{extab:hotspots-1thread-freesurfer-reconall}
\csvtable{tables/hotspots-32threads-freesurfer-reconall.csv}{FreeSurfer recon-all (32 threads): Top functions accouting for 80\% of the application makespan.}{extab:hotspots-32threads-freesurfer-reconall}

% FSL FAST
\csvtable{tables/hotspots-1thread-fsl-fast.csv}{FSL FAST (1 thread): Top functions accouting for 80\% of the application makespan.}{extab:hotspots-1thread-fsl-fast}

% FSL FLIRT
\csvtable{tables/hotspots-1thread-fsl-flirt.csv}{FSL FLIRT (1 thread): Top functions accouting for 80\% of the application makespan.}{extab:hotspots-1thread-fsl-flirt}

% FSL MCFLIRT
\csvtable{tables/hotspots-1thread-fsl-mcflirt.csv}{FSL MCFLIRT (1 thread): Top functions accouting for 80\% of the application makespan.}{extab:hotspots-1thread-fsl-mcflirt}
